No need to know: astrophysics-agnostic gravitational wave cosmology

### 2024-03-11 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/O5_GP_pm.pdf}
    \caption{Spectral siren measurement for an \ac{O5}-like catalog with the ``correct'' parametric model (\plp, green), an ``incorrect'' parametric model (broken power law, orange) and the non-parametric model presented in this work (\acl{Gaussian process}, blue).
    The left panel shows the recovered source frame primary mass distribution for each model, and the simultaneously-inferred posteriors on \Ho{} are shown in the right panel.
    The mass distribution and \Ho{} value used to generate the data are shown by a solid black line in each panel. 
    The ``incorrect'' parametric model fails to recover the true mass distribution and therefore produces a biased estimate of \Ho{}, whereas both the ``correct'' and non-parametric models recover  the mass distribution and \Ho{}.
    As the true mass distribution is unknown, using a non-parametric model mitigates the systematic uncertainty from mismodeling the \ac{CBC} population, though it does introduce additional statistical uncertainty.
    }
    \label{fig:O5_GP}
    \script{nonparametric_twopanel.py}
\end{figure*}

>>>>

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/O5_GP_pm.pdf}
    \caption{Spectral siren measurement for an \ac{O5}-like catalog with the ``correct'' parametric model (\plp, green), an ``incorrect'' parametric model (broken power law, orange) and the non-parametric model presented in this work (\acl{GP}, blue).
    The left panel shows the recovered source frame primary mass distribution for each model, and the simultaneously-inferred posteriors on \Ho{} are shown in the right panel.
    The mass distribution and \Ho{} value used to generate the data are shown by a solid black line in each panel. 
    The ``incorrect'' parametric model fails to recover the true mass distribution and therefore produces a biased estimate of \Ho{}, whereas both the ``correct'' and non-parametric models recover  the mass distribution and \Ho{}.
    As the true mass distribution is unknown, using a non-parametric model mitigates the systematic uncertainty from mismodeling the \ac{CBC} population, though it does introduce additional statistical uncertainty.
    }
    \label{fig:O5_GP}
    \script{nonparametric_twopanel.py}
\end{figure*}
